AbxD01 Analysis

### 2014-12-03 abxD01_analysis.Rmd
used leaps r pkg to determine top linear models

The script for running this code is called "abxD01.lmModel.compare.R". The input files for this script are:
1. abxD01.final.an.unique_list.0.03.subsample.filter16mintotal.shared.topdose2.logtrans.15otus.rfnegpos.csv

I realize I could've done the modelling comparison script in a loop and shortened the code length significantly, but deal with it.

>>>>

The script for running this code is called "abxD01.lmModel.compare2.R". The input files for this script are:
1. abxD01.final.an.unique_list.0.03.subsample.filter16mintotal.shared.topdose2.logtrans.15otus.rfnegpos.csv

I found a program "leaps" in r which will calculate all subsets of a model for a given range of parameters in the model. That is what is used in the above .R file. The methods I used were an exhaustive search and sequential replacement, which is a combination of both forward and backward stepwise directions for model building.  Both of these methods produced similar results. Interestingly, the top models in both methods included 5 common OTUs: 6, 7, 20, 39, and 283 corresponding to a porphyromonadaceae, porphyromonadaceae, alistipes, lachnospiraceae, and blautia OTU respectively.  The blautia OTU is the only one in the group positively (though low and not significantly) correlated with *C. difficile* CFU. There are also several OTUs from the candidate list that did not appear in the top models.
